---
title: "pro"
output: html_document
---

## reading the dataset
```{r }
data <- read.csv("data.csv")
str(data)
head(data)
tail(data)
```

## checking for the null values
```{r }
sum(is.na(data))
data$Date <- as.character.Date(data$Date)
sum(is.na(data$Date))
```


## checking the null values column wise
```{r }
sum(is.na(data$Year))
sum(is.na(data$Type))
sum(is.na(data$Date))
sum(is.na(data$Time))
sum(is.na(data$Place))
sum(is.na(data$Latitude))
sum(is.na(data$Longitude))
sum(is.na(data$ï..Police.Station))
```


```{r }
df <- as.data.frame(table(data$Year))
df$Var1 <- as.numeric(df$Var1)
cor(df$Var1,df$Freq)
```


```{r }
str(data)
```

```{r }
unique(data$Type)
```


```{r }
library(dplyr)
df <- data %>%
  group_by(data$Year) %>%
  summarize(no_of_crimes = n())
df
```

```{r }
plot(df)
```

```{r }
library(forecast)
library(tseries)
yearly <- ts(df$no_of_crimes,start = c(2015,1))
plot(yearly)
acf(yearly)
datamodel = auto.arima(yearly,ic="aic",trace = TRUE)
dataf = forecast(datamodel,level=c(95),h=5)
dataf
plot(dataf)
accuracy(dataf)
```
## year wise murders
```{r }
df1 <- data %>%
  filter(data$Type == "Murder")
df1 <- df1 %>%
  group_by(df1$Year) %>%
  summarize(no_of_crimes = n())
df1
yearly <- ts(df1$no_of_crimes,start = c(2015,1))
plot(yearly)
acf(yearly)
datamodel = auto.arima(yearly,ic="aic",trace = TRUE)
dataf = forecast(datamodel,level=c(95),h=5)
plot(dataf)
dataf
accuracy(dataf)
```

## year wise Attempted Murder
```{r }
df2 <- data %>%
  filter(data$Type == "Attempted Murder")
df2 <- df2 %>%
  group_by(df2$Year) %>%
  summarize(no_of_crimes = n())
df2
yearly <- ts(df2$no_of_crimes,start = c(2015,1))
plot(yearly)
acf(yearly)
datamodel = auto.arima(yearly,ic="aic",trace = TRUE)
dataf = forecast(datamodel,level=c(95),h=5)
dataf
accuracy(dataf)
plot(dataf)
```

## year wise Robbery
```{r }
df3 <- data %>%
  filter(data$Type == "Robbery")
df3 <- df3 %>%
  group_by(df3$Year) %>%
  summarize(no_of_crimes = n())
df3
yearly <- ts(df3$no_of_crimes,start = c(2015,1))
plot(yearly)
acf(yearly)
datamodel = auto.arima(yearly,ic="aic",trace = TRUE)
dataf = forecast(datamodel,level=c(95),h=5)
plot(dataf)
accuracy(dataf)
dataf
```


## year wise Chain Snatching
```{r }
df4 <- data %>%
  filter(data$Type == "Chain Snatching")
df4 <- df4 %>%
  group_by(df4$Year) %>%
  summarize(no_of_crimes = n())
df4
yearly <- ts(df4$no_of_crimes,start = c(2015,1))
plot(yearly)
acf(yearly)
datamodel = auto.arima(yearly,ic="aic",trace = TRUE)
dataf = forecast(datamodel,level=c(95),h=5)
plot(dataf)
dataf
accuracy(dataf)
```


## year wise 2 wheeler theft
```{r }
df5 <- data %>%
  filter(data$Type == "2 wheeler theft")
df5 <- df5 %>%
  group_by(df5$Year) %>%
  summarize(no_of_crimes = n())
df5
yearly <- ts(df5$no_of_crimes,start = c(2015,1))
plot(yearly)
acf(yearly)
datamodel = auto.arima(yearly,ic="aic",trace = TRUE)
dataf = forecast(datamodel,level=c(95),h=5)
dataf
plot(dataf)
accuracy(dataf)
```

## year wise Ordinary Theft
```{r }
df6 <- data %>%
  filter(data$Type == "Ordinary Theft")
df6 <- df6 %>%
  group_by(df6$Year) %>%
  summarize(no_of_crimes = n())
df6
yearly <- ts(df6$no_of_crimes,start = c(2015,1))
plot(yearly)
acf(yearly)
datamodel = auto.arima(yearly,ic="aic",trace = TRUE)
dataf = forecast(datamodel,level=c(95),h=5)
plot(dataf)
dataf
accuracy(dataf)
```

## year wise 4 Wheeler Theft
```{r }
df7 <- data %>%
  filter(data$Type == "4 Wheeler Theft")
df7 <- df7 %>%
  group_by(df7$Year) %>%
  summarize(no_of_crimes = n())
df7
yearly <- ts(df7$no_of_crimes,start = c(2015,1))
plot(yearly)
acf(yearly)
datamodel = auto.arima(yearly,ic="aic",trace = TRUE)
dataf = forecast(datamodel,level=c(95),h=5)
plot(dataf)
dataf
accuracy(dataf)
```

## year wise Kidnap
```{r }
df8 <- data %>%
  filter(data$Type == "Kidnap")
df8 <- df8 %>%
  group_by(df8$Year) %>%
  summarize(no_of_crimes = n())
df8
yearly <- ts(df8$no_of_crimes,start = c(2015,1))
plot(yearly)
acf(yearly)
datamodel = auto.arima(yearly,ic="aic",trace = TRUE)
dataf = forecast(datamodel,level=c(95),h=5)
plot(dataf)
dataf
accuracy(dataf)
```

## year wise Rape
```{r }
df9 <- data %>%
  filter(data$Type == "Rape")
df9 <- df9 %>%
  group_by(df9$Year) %>%
  summarize(no_of_crimes = n())
df9
yearly <- ts(df9$no_of_crimes,start = c(2015,1))
plot(yearly)
acf(yearly)
datamodel = auto.arima(yearly,ic="aic",trace = TRUE)
dataf = forecast(datamodel,level=c(95),h=5)
plot(dataf)
dataf
accuracy(dataf)
```

## year wise Assault
```{r }
df10 <- data %>%
  filter(data$Type == "Assault")
df10 <- df10 %>%
  group_by(df10$Year) %>%
  summarize(no_of_crimes = n())
df10
yearly <- ts(df10$no_of_crimes,start = c(2015,1))
plot(yearly)
acf(yearly)
datamodel = auto.arima(yearly,ic="aic",trace = TRUE)
dataf = forecast(datamodel,level=c(95),h=5)
plot(dataf)
dataf
accuracy(dataf)
```
## we could not make much forecasting yearly

## monthly
```{r }
library(dplyr)
library(tidyr)
data <- data %>%
  separate(Date,c("date","month","year"))
head(data)
```



```{r }
data$Year <- as.integer(data$Year)
data$date <- as.integer(data$date)
data$month <- as.integer(data$month)
data$year <- as.integer(data$year)
data <- data %>%
  mutate(month=replace(month,is.na(month),12))
#sum(is.na(data$month))
data <- data %>%
  mutate(month=ifelse(month >12,ifelse(month %% 10 == 0,month/10,month %% 10),month))
data1 <- data %>%
  group_by(Year,month) %>%
  summarize(cases = n())
data1 <- data1 %>%
  filter(month > 0)
head(data1)
```


```{r }
monthly <- ts(data1$cases,start = c(1,1))
plot(monthly)
acf(monthly)
datamodel = auto.arima(monthly,ic="aic",trace = TRUE)
dataf = forecast(datamodel,level=c(95),h=24)
plot(dataf)
dataf
accuracy(dataf)
```

## Murder
```{r }
unique(data$Type)
data2 <- data %>%
  filter(month > 0 & Type =="Murder") %>%
  group_by(Year,month) %>%
  summarize(cases = n())
murder <- ts(data2$cases,start = c(1,1))
plot(murder)
acf(murder)
datamodel = auto.arima(murder,ic="aic",trace = TRUE)
dataf = forecast(datamodel,level=c(95),h=24)
plot(dataf)
dataf
```


## Murder
```{r }
data3 <- data %>%
  filter(month > 0 & Type =="Attempted Murder") %>%
  group_by(Year,month) %>%
  summarize(cases = n())
Attempted_Murder <- ts(data3$cases,start = c(1,1))
plot(Attempted_Murder)
acf(Attempted_Murder)
datamodel = auto.arima(Attempted_Murder,ic="aic",trace = TRUE)
dataf = forecast(datamodel,level=c(95),h=24)
plot(dataf)
dataf
```


## Robbery
```{r }
data4 <- data %>%
  filter(month > 0 & Type =="Robbery") %>%
  group_by(Year,month) %>%
  summarize(cases = n())
Robbery <- ts(data4$cases,start = c(1,1))
plot(Robbery)
acf(Robbery)
datamodel = auto.arima(Robbery,ic="aic",trace = TRUE)
dataf = forecast(datamodel,level=c(95),h=24)
plot(dataf)
dataf
```

## Chain Snatching
```{r }
data5 <- data %>%
  filter(month > 0 & Type =="Chain Snatching") %>%
  group_by(Year,month) %>%
  summarize(cases = n())
Chain_Snatching <- ts(data5$cases,start = c(1,1))
plot(Chain_Snatching)
acf(Chain_Snatching)
datamodel = auto.arima(Chain_Snatching,ic="aic",trace = TRUE)
dataf = forecast(datamodel,level=c(95),h=24)
plot(dataf)
dataf
```

## 2 wheeler theft
```{r }
data6 <- data %>%
  filter(month > 0 & Type =="2 wheeler theft") %>%
  group_by(Year,month) %>%
  summarize(cases = n())
two_wheeler_theft <- ts(data6$cases,start = c(1,1))
plot(two_wheeler_theft)
acf(two_wheeler_theft)
datamodel = auto.arima(two_wheeler_theft,ic="aic",trace = TRUE)
dataf = forecast(datamodel,level=c(95),h=24)
plot(dataf)
dataf
accuracy(dataf)
```

## Ordinary Theft
```{r }
data7 <- data %>%
  filter(month > 0 & Type =="Ordinary Theft") %>%
  group_by(Year,month) %>%
  summarize(cases = n())
OrdinaryTheft <- ts(data7$cases,start = c(1,1))
plot(OrdinaryTheft)
acf(OrdinaryTheft)
datamodel = auto.arima(OrdinaryTheft,ic="aic",trace = TRUE)
dataf = forecast(datamodel,level=c(95),h=24)
plot(dataf)
dataf
accuracy(dataf)
```

## Robbery
```{r }
data4 <- data %>%
  filter(month > 0 & Type =="Robbery") %>%
  group_by(Year,month) %>%
  summarize(cases = n())
Robbery <- ts(data4$cases,start = c(1,1))
plot(Robbery)
acf(Robbery)
datamodel = auto.arima(Robbery,ic="aic",trace = TRUE)
dataf = forecast(datamodel,level=c(95),h=24)
plot(dataf)
dataf
unique(data$Type)
```

```{r }
data7 <- data %>%
  filter(month > 0 & Type =="Kidnap") %>%
  group_by(Year,month) %>%
  summarize(cases = n())
OrdinaryTheft <- ts(data7$cases,start = c(1,1))
plot(OrdinaryTheft)
acf(OrdinaryTheft)
datamodel = auto.arima(OrdinaryTheft,ic="aic",trace = TRUE)
dataf = forecast(datamodel,level=c(95),h=24)
plot(dataf)
dataf
accuracy(dataf)
```


```{r }
data7 <- data %>%
  filter(month > 0 & Type =="Assault") %>%
  group_by(Year,month) %>%
  summarize(cases = n())
OrdinaryTheft <- ts(data7$cases,start = c(1,1))
plot(OrdinaryTheft)
acf(OrdinaryTheft)
datamodel = auto.arima(OrdinaryTheft,ic="aic",trace = TRUE)
dataf = forecast(datamodel,level=c(95),h=24)
plot(dataf)
dataf
accuracy(dataf)
```

```{r }

```